---
title: "Stats 15 - Homework 2"
author: "Haojie Liu"
geometry: "left=2cm,right=2cm,top=1.5cm,bottom=1.5cm"
output: pdf_document
---

Homework text and questions: Copyright Miles Chen. Do not post, share, or distribute without permission.

# Academic Integrity Statement

By modifying this statement, I, Haojie Liu, declare that all of the work in this assignment is my own original work. At no time did I look at the code of other students nor did I search for code solutions online. I understand that plagiarism on any single part of this assignment will result in a 0 for the entire assignment and that I will be referred to the dean of students.

```{r, echo = FALSE}
library(knitr)
library(tidyverse)
```

# Part 1: Textbook, Section 4.4, Exercise 1

The subset of the `babynames` data has been recreated for you here:

```{r}
year <- c(2003, 1999, 2010, 1989, 1989, 1928, 1981, 1981, 1920, 1941)
sex <- c("M", "F", "F", "F", "F", "M", "F", "F", "F", "M")
name <- c("Bilal","Terria","Naziyah","Shawana","Jessi","Tillman","Leslee",
          "Sherise","Marquerite","Lorraine")
n <- as.integer(c(146, 23, 45, 41, 210, 43, 83, 27, 26, 24))
prop <- c(0.0000695, 0.0000118, 0.0000230, 0.0000206, 0.000105 , 0.0000377, 
          0.0000464, 0.0000151, 0.0000209, 0.0000191)
baby_subset <- tibble(year, sex, name, n, prop)
print(baby_subset)
```

Execute the appropriate `dplyr` commands that will recreate the output you see in the textbook.

a. 
```{r, error = TRUE}
baby_subset %>% 
  select(year,sex,name, n) %>% 
  filter(n %in% 41:83)
```

b.
```{r}
baby_subset %>% 
  filter(nchar(name) == 6)
```

c.

```{r}

baby_subset %>% 
  filter(year == 1989) %>% 
  mutate(total=n/prop)

```

d.

```{r}
baby_subset %>% 
  group_by(year) %>% 
  summarize(
    total = sum(n)
  ) %>% 
  select(year, total) %>% 
  arrange(year)
```


# Part 2: Textbook, Section 4.4, Exercise 3

The problem with the pipeline is that there will be no column called "am" after summarize the avg_mpg by mean(mpg). Therefore, filter() should placed before summarize() to filter the data.


# Part 3: Textbook, Section 4.4, Exercise 4

```{r  fig.width = 30, fig.asp = 0.8, out.width = "100%"}
library(Lahman)
Teams %>% 
  tail()


Teams %>% 
  mutate( X1B = H-X2B-X3B-HR) %>% 
  summarize(
    BA = H/AB,
    SLG = ( X1B + 2*X2B + 3*X3B + 4*HR)/AB,
    yearID = yearID,
    teamID = teamID
  ) %>% 
  ggplot(aes(
    x= yearID,
    y= SLG,
    color = teamID 
    ))+geom_point(size=2)+geom_smooth(se =FALSE)
```

```{r  fig.width = 30, fig.asp = 0.8, out.width = "100%"}
Teams %>% 
  mutate( X1B = H-X2B-X3B-HR) %>% 
  summarize(
    BA = H/AB,
    SLG = ( X1B + 2*X2B + 3*X3B + 4*HR)/AB,
    yearID = yearID,
    teamID = teamID
  ) %>% 
  ggplot(aes(
    x= yearID,
    y= BA,
    color = teamID 
    ))+geom_point(size =2)+geom_smooth(se =FALSE)

```

# Part 4: Textbook, Section 4.4, Exercise 7
```{r}
Teams %>% 
  mutate( X1B = H-X2B-X3B-HR) %>% 
  summarize(
    teamID = teamID,
    SLG = ( X1B + 2*X2B + 3*X3B + 4*HR)/AB
  ) %>% 
  arrange(desc(SLG)) %>% 
  head(5)
```
```{r}

Teams %>% 
  filter(yearID >= 1969) %>% 
  mutate( X1B = H-X2B-X3B-HR) %>% 
  summarize(
    teamID = teamID,
    SLG = ( X1B + 2*X2B + 3*X3B + 4*HR)/AB
  ) %>% 
  arrange(desc(SLG)) %>% 
  head(5)
  
```

# Part 5: Textbook, Section 4.4, Exercise 8
a.
```{r}

Teams %>% 
  filter (yearID >= 1954) %>% 
  group_by(lgID) %>% 
  mutate( X1B = H-X2B-X3B-HR) %>% 
  summarise(
    teamID = teamID,
    SLG = ( X1B + 2*X2B + 3*X3B + 4*HR)/AB,
    year = yearID
  ) %>% 
  ggplot(aes(
    x = year,
    y = SLG,
    color = lgID
  ))+geom_point()+
  geom_smooth()
```

AL does have a higher SLG since 1954. According to the graph, most of the time, AL line is above NL line, therefore, it will has a higher mean compare to the others.


# Part 6: Textbook, Section 5.5, Exercise 1

```{r}
statenames <- tibble(names = state.name, twoletter = state.abb)
glimpse(statenames)
```

```{r}
statedata <- tibble(
  names = state.name, 
  income = state.x77[, 2], 
  illiteracy = state.x77[, 3]
  )
glimpse(statedata)
```


```{r  fig.width = 10, fig.asp = 0.8, out.width = "100%"}
library(ggrepel)

statedata <- statedata %>% 
  left_join(statenames, by = c("names" = "names"))

statedata %>% 
  ggplot(aes(
    x = illiteracy,
    y = income,
    color = names
  ))+
  geom_point()+
  geom_text_repel(data = statedata, aes(label = twoletter))+
  geom_smooth(se = FALSE)
```



# Part 7: Textbook, Section 5.5, Exercise 2


Part a. 

```{r}

Batting %>% 
  group_by(playerID) %>% 
  summarise(
    total_HR = sum(HR),
    total_SB = sum(SB)
  ) %>% 
  right_join(People, by = c("playerID" = "playerID")) %>% 
  filter(total_HR >= 300 ) %>% 
  filter(total_SB >= 300) %>% 
  select(playerID, nameFirst, nameLast, nameGiven, total_HR, total_SB)
  

```


Part b.

```{r}
Pitching %>% 
  group_by(playerID) %>% 
  summarise(
    total_W = sum(W),
    total_SO = sum(SO)
  ) %>% 
  right_join(People, by = c("playerID" = "playerID")) %>% 
  filter(total_W >= 300 ) %>% 
  filter(total_SO >= 3000) %>% 
  select(playerID, nameFirst, nameLast, nameGiven, total_W, total_SO)

```


Part c.

```{r}
Batting %>%
  group_by(playerID, yearID) %>%
  summarize(
    TotalHR = sum(HR), 
    BA = sum(H)/sum(AB
    )) %>%
  right_join(People, by = c("playerID" = "playerID")) %>%
  filter(TotalHR >= 50) %>%
  select( yearID, nameFirst, nameLast, nameGiven, TotalHR, BA) %>%
  arrange(BA)


```
Pete Alonso in 2019 has the lowest batting average

